ODGI: scalable tools for pangenome graphs

### 2021-06-01 manuscript/main.tex
First authors - only one correspondent
In an app note we say features
Changed font for cmd

\newcommand{\odgi}{ODGI}
\newcommand{\cmd}[1]{{\texttt{#1}}}
\newcommand{\cmdbf}[1]{{\textbf{#1}}}
\newcommand{\topic}[1]{{\cmdbf{#1}}:}
\newcommand{\Rplus}{\protect\hspace{-.1em}\protect\raisebox{.35ex}{\smaller{\smaller\textbf{+}}}}
\newcommand{\pp}{\Rplus\Rplus}
\newcommand{\Cpp}{\mbox{C\Rplus\Rplus}\xspace}

@@

    \corresp{$^\ast$To whom correspondence should be addressed.}
    \corresp{$^\dagger$Shared first authorship.}

@@

    \abstract{
        \textbf{Motivation:} Pangenome graphs provide a complete representation of
        genomic information that allows for complex population-sized analysis of genomes
        without introducing reference genome bias.
        %
        \\
        \textbf{Results:} Here we present \odgi\, a novel range of tools that makes use of an efficient
        in-memory representation of DNA graphs structured in the variation graph model. \odgi\ can
        handle hundreds of large genomes while maintaining fast execution runtime and low memory overhead.
        \odgi\ includes tools for detecting complex regions, extracting \textit{loci}, exploratory analysis,
        sorting, removing artifacts, and graphs manipulation and visualisation.
        %
        \\
        \textbf{Availability:} \odgi\ is software written in the \Cpp\ programming language and
        published under the libre MIT license. Source code and user manual can be downloaded from
        \href{https://github.com/pangenome/odgi}{https://github.com/pangenome/odgi}.\\
        %
        \textbf{Contact:}
        \href{andreaguarracino@outlook.com}{andreaguarracino@outlook.com},
        \href{erik.garrison@gmail.com}{erik.garrison@gmail.com}\\
        \textbf{Supplementary information:} Supplementary data are available at \textit{Bioinformatics} online.}

@@

    \section{Results}

@@

    \topic{odgi build, view \& validate} pangenome graphs are
    represented by a subset of the textual Graphical Fragment Assembly
    (GFAv1) format\citep{GFAv1}; \cmd{odgi build} and \cmd{odgi view}
    convert graphs from GFA to the \odgi\ format and vice versa.
    \cmd{odgi validate} ascertains the graph data is correct, such as
    validating that paths respect the graph's topology.

>>>>

\newcommand{\odgi}{ODGI}
\newcommand{\cmd}[1]{{\scriptsize\textrm{#1}}}
\newcommand{\cmdbf}[1]{{\textbf{#1}}}
\newcommand{\topic}[1]{{\cmdbf{#1}}:}
\newcommand{\Rplus}{\protect\hspace{-.1em}\protect\raisebox{.35ex}{\smaller{\smaller\textbf{+}}}}
\newcommand{\pp}{\Rplus\Rplus}
\newcommand{\Cpp}{\mbox{C\Rplus\Rplus}\xspace}

@@

    \corresp{$^\ast$To whom correspondence should be addressed.}
    \corresp{$^\dagger$The authors wish it to be known that the first two authors should be regarded as joint First Authors.}

@@

    \abstract{
        \textbf{Motivation:} Pangenome graphs provide a complete representation of
        genomic information that allows for complex population-sized analysis of genomes
        without introducing reference genome bias.
        %
        \\
        \textbf{Results:} Here we present \odgi\, a novel range of tools that makes use of an efficient
        in-memory representation of DNA graphs structured in the variation graph model. \odgi\ can
        handle hundreds of large genomes while maintaining fast execution runtime and low memory overhead.
        \odgi\ includes tools for detecting complex regions, extracting \textit{loci}, exploratory analysis,
        sorting, removing artifacts, and graphs manipulation and visualisation.
        %
        \\
        \textbf{Availability:} \odgi\ is software written in the \Cpp\ programming language and
        published under the libre MIT license. Source code and user manual can be downloaded from
        \href{https://github.com/pangenome/odgi}{https://github.com/pangenome/odgi}.\\
        %
        \textbf{Contact:}
        % \href{andreaguarracino@outlook.com}{andreaguarracino@outlook.com},
        \href{erik.garrison@gmail.com}{erik.garrison@gmail.com}\\
        \textbf{Supplementary information:} Supplementary data are available at \textit{Bioinformatics} online.}

@@

    \section{Features}

@@

    \topic{odgi build, view \& validate} pangenome graphs are
    represented by a subset of the textual Graphical Fragment Assembly
    (GFAv1) format\citep{GFAv1}; \cmd{odgi build} and \cmd{odgi view}
    convert graphs from GFA to the \odgi\ format and \textit{vice versa}.
    \cmd{odgi validate} ascertains the graph data is correct, such as
    validating that paths respect the graph's topology.
